Computer Science House Constitution

### 2022-02-15 constitution.tex
Reword Elections and Requirements

		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will record the reason with the absence.

>>>>

		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will note is as an Absence with Reason.
